The \dealii{} Library, Version 9.0

### 2018-04-07 9.0/paper.tex
Use math syntax in two places.

The major changes of this release are:
\begin{itemize}
\item
  Manifold smoothing: The manifold smoothing algorithms applied in the
  Triangulation class and MappingQGeneric have been changed from the old
  Laplace-style smoothing to a transfinite interpolation that linearly
  blends between the descriptions on the faces around a cell. The old
  transformation introduced boundary layers inside cells that prevented
  convergence rates from exceeding 3.5 in the global L2 errors on typical
  settings. This change also considerably improves mesh quality on settings
  where curved descriptions are only applied to the boundary rather than
  the whole volume.

>>>>

The major changes of this release are:
\begin{itemize}
\item
  Manifold smoothing: The manifold smoothing algorithms applied in the
  Triangulation class and MappingQGeneric have been changed from the old
  Laplace-style smoothing to a transfinite interpolation that linearly
  blends between the descriptions on the faces around a cell. The old
  transformation introduced boundary layers inside cells that prevented
  convergence rates from exceeding \(3.5\) in the global \(L^2\) errors on typical
  settings. This change also considerably improves mesh quality on settings
  where curved descriptions are only applied to the boundary rather than
  the whole volume.
